BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-03 tex/3-algorithms.tex
Small changes after skype call + end of algorithms section.

% html extraction is not trival
extracting metadata and content from html documents is a challenging task. standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}. for instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. more recently, specifications such as microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. in fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass html validation\cite{brianwilson2008-a}. under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.

\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these assumptions, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}

% assumptions when working with blogs
Having blogs as our target websites, we use the following observations \TODO{If ok, change everywhere else.} which play a central role in the extraction process\Anote{assumptions}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs. \TODO{Add more info on web feeds, merge with the text on intro?} Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.

@@

% input from assumptions.
Assumption \ref{havefeedAssum} allows the crawler to obtain input for the algorithm: each entry of the web feed provides a link to the corresponding we page as well as potential target content such as the article, it's title, authors and publication date. Assumption \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.

@@

% into: algo 1 defined
With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis which will show that this aproach has a quadratic running time.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates and comments}
\label{variationsforauthorsdatesandcomments}

% intro
In the current state algorithms \ref{extractionAlgo} and \ref{linearAlgo} will perform poorly for author and date extraction and are not suitable for comment extraction. This subsection presents variations on the general extraction
\label{presentsvariationsonthegeneralextraction}techniques presented before. \TODO{Rephrase this to say that we don't show the full algos because it's just as in the 2 previous with customised score function!}Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.

@@

\TODO{rush some time complexity analysis and conclude that we can do optimization analogs to algo 2 to obtain linear time on each extraction algo. }

>>>>

% html extraction is not trival
extracting metadata and content from html documents is a challenging task. standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}. for instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. more recently, specifications such as microdata\cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\%\cite{andrewrogers2013} of websites. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages\cite{brianwilson2008}, and more than 95\% of pages do not pass html validation\cite{brianwilson2008-a}. under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.

\Anotecontent{observations}{Our experiments on a large dataset of blogs showed that failing tests were either due to a violation of one of these observations, or to an insufficient amount of text in posts, such as \emph{photoblogs} with short captions.}

% observations when working with blogs
Having blogs as our target websites, we use the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 posts\cite{oita2010}, often less than the total number of posts in blogs. Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in the feed.

@@

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain input for the algorithm: each entry of the web feed provides a link to the corresponding we page as well as potential target content such as the article, it's title, authors and publication date. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all the posts of a blog.

@@

% into: algo 1 defined
With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis which will show that this aproach has a quadratic running time.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates, comments}
\label{variationsforauthorsdatesandcomments}

% intro
Using string similarity as only score measurement leads to poor performances on authors and dates extraction and is not suitable for comment extraction. This subsection presents variations of the previously presented \code{ScoreFunction} which address issues of these other contents.

@@

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of all nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity. While evaluating rules for comments extraction requires more a expensive algorithm, the proportion of candidates left after filter out comment rules with an insufficient number of results was very low in practice. Analog  reformulations to the one explained in \ref{timecomplexityandlinearreformulation} can be applied for each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-03 tex/5-evaluation.tex
3.2 fixed.
Small changes after skype call + end of algorithms section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{python-readability2011}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{goose2012}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (assumptions \ref{havefeedAssum} and \ref{similarhtmlAssum}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction running times}

% running time eval, scalability with size of blogs
In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest will be the scalability of extraction procedures as the number of processes pages increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published data on a blog.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate of post content and title extraction we compared our approach to three open source projects: Readability\cite{python-readability2011}, Boilerpipe\cite{kohlschuetter2010} and Goose\cite{goose2012}. These projects are more generic than our blog specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of a same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction running times}

% running time eval, scalability with size of blogs
In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest will be the scalability of extraction procedures as the number of processed pages increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published data on a blog.

@@

\TODO{make a paragraph with linux, python and processor}
